\section*{Additional publications co-authored during the PhD study}

%\nocite{*}
%\begingroup
%\renewcommand{\chapter}[2]{}%
%\renewcommand{\chapter}[2]{}% for other classes
%\bibliographystyle{plainyr-rev}
%\bibliographystyle{sortbyyear_natbib}
%\bibliography{papers2}
%\endgroup
\begin{itemize}

%\bibitem{Brejnholt:14}
\item
Nicolai~F. Brejnholt, Regina Soufli, Marie-Anne Descalle, M\'{o}nica
  Fern\'{a}ndez-Perea, Finn~E. Christensen, Anders~C. Jakobsen, Veijo
  Honkim\"{a}ki, and Michael~J. Pivovaroff.
\newblock Demonstration of multilayer reflective optics at photon energies
  above 0.6 mev.
\newblock {\em Opt. Express}, 22(13):15364--15369, Jun 2014.

%\bibitem{doi:10.1117/12.2055920}
\item
Marcos Bavdaz, Eric Wille, Kotska Wallace, Brian Shortt, Sebastiaan Fransen,
  Maximilien Collon, Marcelo Ackermann, Giuseppe Vacanti, Ramses Guenther,
  Jeroen Haneveld, Mark~Olde Riekerink, Coen van Baren, Dirk Kampf, Karl-Heinz
  Zuknik, Finn Christensen, Desiree Della Monica~Ferreira, Anders~Clemen
  Jakobsen, Michael Krumrey, Peter M\"{u}ller, Vadim Burwitz, Giovanni
  Pareschi, and Mauro Ghigo.
\newblock Preparing the optics technology to observe the hot universe.
\newblock {\em Proc. SPIE}, 9144:91442F--91442F--8, 2014.

%\bibitem{doi:10.1117/12.2055183}
\item
R.~Willingale, G.~Pareschi, F.~Christensen, J.-W. den Herder, D.~Ferreira,
  A.~Jakobsen, M.~Ackermann, M.~Collon, and M.~Bavdaz.
\newblock Science requirements and optimization of the silicon pore optics
  design for the athena mirror.
\newblock {\em Proc. SPIE}, 9144:91442E--91442E--9, 2014.

%\bibitem{Irastorza:2013jv}
\item
I~G Irastorza, F~T Avignone, G~Cantatore, J~M Carmona, S~Caspi, S~A Cetin,
  F.~E. Christensen, A~Dael, T~Dafni, M~Davenport, A~V Derbin, K~Desch,
  A~Diago, B~D{\"o}brich, A~Dudarev, C~Eleftheriadis, G~Fanourakis,
  E~Ferrer-Ribas, J~Galan, J~A Garcia, J~G Garza, T~Geralis, B~Gimeno,
  I~Giomataris, S~Gninenko, H~Gomez, E~Guendelman, C~J Hailey, T~Hiramatsu,
  D~H~H Hoffmann, D~Horns, F~J Iguaz, J~Isern, A.~C. Jakobsen, J~Jaeckel,
  K~Jakovcic, J~Kaminski, M~Kawasaki, M~Krcmar, C~Krieger, B~Lakic, A~Lindner,
  A~Liolios, G~Luzon, I~Ortega, T~Papaevangelou, M~J Pivovaroff, G~Raffelt,
  J~Redondo, A~Ringwald, S~Russenschuck, J~Ruz, K~Saikawa, I~Savvidis,
  T~Sekiguchi, I~Shilon, P~Sikivie, H~Silva, H~Ten~Kate, A~Tomas, S~Troitsky,
  T~Vafeiadis, K~van Bibber, P~Vedrine, J~A Villar, J~K Vogel, L~Walckiers,
  W~Wester, S~C Yildiz, and K~Zioutas.
\newblock {Future axion searches with the International Axion Observatory
  (IAXO)}.
\newblock {\em Journal of Physics: Conference Series}, 460(1):012002, October
  2013.

%\bibitem{Bavdaz:2013ce}
\item
Marcos Bavdaz, Eric Wille, Kotska Wallace, Brian Shortt, Sebastiaan Fransen,
  Nicola Rando, Maximilien Collon, Marcelo Ackermann, Giuseppe Vacanti, Ramses
  G{\"u}nther, Jeroen Haneveld, Mark~Olde Riekerink, Arenda Koelewijn, Coen van
  Baren, Dirk Kampf, Karl-Heintz Zuknik, Arnd Reutlinger, Finn Christensen,
  Desiree Della Monica~Ferreira, Anders~C Jakobsen, Michael Krumrey, Peter
  M{\"u}ller, Vadim Burwitz, Giovanni Pareschi, Mauro Ghigo, Marta Civitani,
  Laura Proserpio, Daniele Spiga, Stefano Basso, Bianca Salmaso, Daniele
  Gallieni, Matteo Tintori, Pierluigi Fumi, Francesco Martelli, Giancarlo
  Parodi, Ivan Ferrario, and Ian Povey.
\newblock { X-ray optics developments at ESA}.
\newblock In {\em SPIE Optical Engineering + Applications}, pages
  88610L--88610L--12. International Society for Optics and Photonics, September
  2013.

%\bibitem{FernandezPerea:2013jb}
\item
Monica Fernandez-Perea, Marie-Anne Descalle, Regina Soufli, Klaus~P Ziock,
  Jennifer Alameda, Sherry~L Baker, Tom~J McCarville, Veijo Honkim{\"a}ki, Eric
  Ziegler, Anders~C Jakobsen, Finn~E Christensen, and Michael~J Pivovaroff.
\newblock {Physics of Reflective Optics for the Soft Gamma-Ray Photon Energy
  Range}.
\newblock {\em Physical Review Letters}, 111(2):027404, July 2013.

%\bibitem{ferreira2013hard}
\item
Desiree Della~Monica Ferreira, Finn~E Christensen, Michael~J Pivovaroff,
  Nicolai Brejnholt, Monica Fernandez-Perea, Niels J{\o}rgen~S Westergaard,
  Anders~C Jakobsen, Marie-Anne Descalle, Regina Soufli, and Julia~K Vogel.
\newblock {Hard x-ray/soft gamma ray telescope designs for future astrophysics
  missions}.
\newblock In {\em SPIE Optical Engineering+ Applications}, pages
  886116--886116. International Society for Optics and Photonics, 2013.

%\bibitem{ferreira2013coating}
\item
Desiree~DM Ferreira, Finn~E Christensen, Anders~C Jakobsen, Niels~J
  Westergaard, and Brian Shortt.
\newblock {Coating optimization for the ATHENA+ mission}.
\newblock In {\em SPIE Optical Engineering+ Applications}, pages
  886112--886112. International Society for Optics and Photonics, 2013.

%\bibitem{FernandezPerea:2012fj}
\item
Monica Fernandez-Perea, Mike~J Pivovaroff, Regina Soufli, Jennifer Alameda,
  Paul Mirkarimi, Marie-Anne Descalle, Sherry~L Baker, Tom McCarville, Klaus
  Ziock, Donald Hornback, Suzanne Romaine, Ric Bruni, Zhong Zhong, Veijo
  Honkim{\"a}ki, Eric Ziegler, Finn~E Christensen, and Anders~C Jakobsen.
\newblock {Ultra-short-period WC/SiC multilayer coatings for x-ray
  applications}.
\newblock {\em Nuclear Instruments {\&} Methods In Physics Research Section
  A-Accelerators Spectrometers Detectors And Associated Equipment}, October
  2012.

%\bibitem{ferreira2012athena}
\item
Desiree~DM Ferreira, Finn~E Christensen, Anders~C Jakobsen, Niels~J
  Westergaard, and Brian Shortt.
\newblock {ATHENA optimized coating design}.
\newblock In {\em SPIE Astronomical Telescopes+ Instrumentation}, pages
  84435L--84435L. International Society for Optics and Photonics, 2012.

%\bibitem{Christensen:2011wg}
\item
Finn~E Christensen, Anders~C Jakobsen, Nicolai~F Brejnholt, Kristin~K Madsen,
  Allan Hornstrup, Niels~J Westergaard, Joan Momberg, Jason Koglin, Anne~M
  Fabricant, Marcela Stern, William~W Craig, Michael~J Pivovaroff, and David
  Windt.
\newblock {Coatings for the NuSTAR mission}.
\newblock In {\em SPIE Optical Engineering+ Applications}, pages
  81470U--81470U--19, September 2011.

%\bibitem{Koglin:2011gu}
\item
Jason~E Koglin, Hongjun An, Nicolas Barriere, Nicolai~F Brejnholt, Finn~E
  Christensen, William~W Craig, Charles~J Hailey, Anders~Clemen Jakobsen,
  Kristin~K Madsen, Kaya Mori, Melania Nynka, Monica Fernandez-Perea, Michael~J
  Pivovaroff, Andrew Ptak, Clio Sleator, Doug Thornhill, Julia~K Vogel,
  Daniel~R Wik, and William~W Zhang.
\newblock {First results from the ground calibration of the NuSTAR flight
  optics}.
\newblock {\em SPIE Optical Engineering + Applications},
  8147:81470J--81470J--16, September 2011.

%\bibitem{Todd:2011vk}
\item
Nicolai Brejnholt, Finn~Erland Christensen, Charles~J Hailey, Nicolas~M
  Barri{\`e}re, William~W Craig, Brian Grefenstette, Jason Koglin,
  Kristin~Kruse Madsen, Julia~K Vogel, Hongjun An, Kenneth Blaedel, Josh Brown,
  Todd Decker, Zeshan Haider, Anders~Clemen Jakobsen, Carsten~P Cooper-Jensen,
  Kaya Mori, Melania Nynka, Michael~J Pivovaroff, Clio Sleator, Dennis
  Stefanik, Marcela Stern, Gordon Tajiri, Douglas Thornhill, and Jeremy~S
  Cushman.
\newblock {The Rainwater Memorial Calibration Facility for X-Ray Optics}.
\newblock {\em X-Ray Optics and Instrumentation}, 2011:285079, 2011.

%\bibitem{7e591012d8514e849088e191bf1d4504}
\item
Nicolai Brejnholt, Finn~Erland Christensen, Anders~Clemen Jakobsen, Charles~J
  Hailey, Jason~E Koglin, Kenneth~L Blaedel, Marcela Stern, Doug Thornhill,
  Clio Sleator, Shuo Zhang, William~W Craig, Kristin~K Madsen, Todd Decker,
  Michael~J Pivovaroff, and Julia~K Vogel.
\newblock {NuSTAR ground calibration: The Rainwater Memorial Calibration
  Facility (RaMCaF)}.
\newblock In {\em SPIE Optical Engineering + Applications}, pages 81470I--9,
  2011.

%\bibitem{collon2011design}
\item
Maximilien~J Collon, Ramses G{\"u}nther, Marcelo Ackermann, Rakesh Partapsing,
  Giuseppe Vacanti, Marco~W Beijersbergen, Marcos Bavdaz, Kotska Wallace, Erik
  Wille, Mark Olde~Riekerink, Jeroen Haneveld, Arenda Koelewijn, Coen van
  Baren, Peter M{\"u}ller, Michael Krumrey, Michael Freyberg, Anders~Clemen
  Jakobsen, and Finn~Erland Christensen.
\newblock {Design, fabrication, and characterization of silicon pore optics for
  ATHENA/IXO}.
\newblock In {\em SPIE Optical Engineering + Applications}, pages 81470D--1,
  2011.

\end{itemize}
