\chapter{Papers included in the thesis}

%% The order of the papers must be A, B, C, ...

\begin{itemize}

\item[{[\ref{pap:PREL_ATHENA}]}]
Anders C. Jakobsen, Desiree Della Monica Ferreira, Finn E. Christensen, Brian Shortt, Max Collon, Marcelo D. Ackermann; Preliminary coating design and coating developments for ATHENA. {\em Proc. SPIE 8147, Optics for EUV, X-Ray and Gamma-Ray Astronomy V}, 81470T (October 06, 2011);

\item[{[\ref{pap:axion_spie}]}]
Anders C. Jakobsen, Michael J. Pivovaroff, Finn E. Christensen;
X-ray optics for axion helioscopes. {\em Proc. SPIE 8861, Optics for EUV, X-Ray and Gamma-Ray Astronomy VI}, 886113 (September 26, 2013)

\item[{[\ref{pap:iaxo_concept}]}]
E Armengaud, F T Avignone, M Betz, P Brax, P Brun, G Cantatore, J M Carmona, G P Carosi, F Caspers, S Caspi, S A Cetin, D Chelouche, F E Christensen, A Dael, T Dafni, M Davenport, A V Derbin, K Desch, A Diago, B D\"{o}brich, I Dratchnev, A Dudarev, C Eleftheriadis, G Fanourakis, E Ferrer-Ribas, J Gal\'{a}n, J A García, J G Garza, T Geralip, B Gimeno, I Giomataris, S Gninenko, H G\'{o}mez, D Gonz\'{a}lez-D\'{i}az, E Guendelman, C J Hailey, T Hiramatsu, D H H Hoffmann, D Horns, F J Iguaz, I G Irastorza, J Isern, K Imai, A C Jakobsen, J Jaeckel, K Jakov\u{c}i\'{c}a, J Kaminski, M Kawasaki, M Karuza, M Kr\u{c}mara, K Kousouris, C Krieger, B Laki\'{c}a, O Limousin, A Lindner, A Liolios, G Luz\'{o}n, S Matsuki, V N Muratova, C Nones, I Ortega, T Papaevangelou, M J Pivovaroff, G Raffelt, J Redondo, A Ringwald, S Russenschuck, J Ruz, K Saikawa, I Savvidis, T Sekiguchi, Y K Semertzidis, I Shilon, P Sikivie, H Silva, H ten Kate, A Tomas, S Troitsky, T Vafeiadis, K van Bibbera, P Vedrine, J A Villar, J K Vogel, L Walckiers, A Weltman, W Wester, S C Yildiz and K Zioutas. Conceptual design of the International Axion Observatory (IAXO). {\em J.\ Inst.} \textbf{9} (2014).




\end{itemize}
